Structuring College Access

### 2025-02-08 index.qmd
update affiliation

---
title: 'Structuring College Access'
subtitle: 'The Market Segment Model and College Board Geomarkets'
author:
  - name: Ozan Jaquette
    affiliation: UCLA
  - name: Karina Salazar
    affiliation: University of Arizona
  - name: Crystal Han
    affiliation: Stanford University
bibliography: ./assets/bib/cb_geomarket_bib.bib
format:
  revealjs: 
    theme: [default, ./assets/css/custom.scss]
    controls: true
    controls-layout: bottom-right
    controls-tutorial: true
    transition: slide
    background-transition: fade
    auto-stretch: false
    slide-level: 3
    menu:
      titleSelector: 'h1, h2, .slide:not(.hide) h3'
      useTextContentForMissingTitles: false
      hideMissingTitles: true
    template-partials:
      - ./assets/html/title-slide.html
include-in-header: ./assets/html/header.html
---

>>>>

---
title: 'Structuring College Access'
subtitle: 'The Market Segment Model and College Board Geomarkets'
author: ['Ozan Jaquette', 'Karina Salazar', 'Crystal Han']
institute: ['UCLA', 'University of Arizona', 'Stanford University']
bibliography: ./assets/bib/cb_geomarket_bib.bib
format:
  revealjs: 
    theme: [default, ./assets/css/custom.scss]
    controls: true
    controls-layout: bottom-right
    controls-tutorial: true
    transition: slide
    background-transition: fade
    auto-stretch: false
    slide-level: 3
    menu:
      titleSelector: 'h1, h2, .slide:not(.hide) h3'
      useTextContentForMissingTitles: false
      hideMissingTitles: true
    template-partials:
      - ./assets/html/title-slide.html
include-in-header: ./assets/html/header.html
---
